ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-11-14 pyked.tex
revision and response about ReSpecTh email to close #46

%% !TEX option = -shell-escape
%% comment out the above line before submitting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is licensed under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by/4.0/.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{ijck}

@@

However, ReSpecTh experimental files are another
XML-based format, and, as such, suffer from the same readability issues as PrIMe.
Moreover, the standard remains inaccessible to the public, requiring potential users
to register with the standard's authors using a valid institutional email address
to access the specification and the growing database.

>>>>

% !TEX option = -shell-escape
%% comment out the above line before submitting
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is licensed under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by/4.0/.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{ijck}

@@

However, ReSpecTh experimental files are another
XML-based format, and, as such, suffer from the same readability issues as PrIMe.
Moreover, \deletetwo{the standard remains inaccessible to the public, requiring potential users
to register with the standard's authors using a valid institutional email address
to access the specification and the growing database}
\addtwo{potential users must register using a valid institutional email address
to access the growing database}.
